---
title: "HW_6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(geofacet)
library(tidyr)
library(lubridate)
```

```{r , echo=TRUE}
#Load house_prices.rda in R
load('/Users/ckalo7/Documents/CSC 302/DATA/house_prices.rda')

#and perform the followings:
```
(a) Use facet_wrap to draw line plots to represent the trend
   for house_price_index over years for each state. Please have
   three ticks on the x axis which are for years 1980, 2000, and
   2020. Since you have limited space your labels can be ’80, ’00,
   and ’20 for these ticks.
```{r , echo=TRUE}
#facet_wrap
ggplot(data=house_prices, aes(x=date, y=house_price_index)) +
  geom_line() +
  geom_point() +
  facet_wrap(~state) +
  scale_y_continuous(
    name = "House Price Index",
  ) +
  scale_x_date(
    name = "Year",
    breaks = ymd(c("1980-01-01", "2000-01-01", "2020-01-01")),
    labels = c("'80", "'00", "'20"),
    expand = c(.1, 0)
  ) +
  coord_cartesian(clip = "on")

#facet_geo
ggplot(data=house_prices, aes(x=date, y=house_price_index)) +
  geom_line() +
  geom_point() +
  facet_geo(~state, grid = "us_state_grid1") +
  scale_y_continuous(
    name = "House Price Index",
  ) +
  scale_x_date(
    name = "Year",
    breaks = ymd(c("1980-01-01", "2000-01-01", "2020-01-01")),
    labels = c("'80", "'00", "'20"),
    expand = c(.1, 0)
  ) +
  coord_cartesian(clip = "on") 
```
(b) Use gather() function from tidyr to reshape your data in a way
   that it will have measure and value columns for house_price_index
   and unemploy_perc, respectively, in two columns. You should leave
   out remaining attributes by using ”-” in front them inside the
   function. Then, direct the output to a new data frame called
   house_reshaped Please refer to examples we did in class.
```{r , echo=TRUE}
house_reshaped <- gather(data=house_prices, key=measure, value=value,
                         -date, -state, -house_price_perc, house_price_index,
                         unemploy_perc)
```
(c) Use house_reshaped to replicate the graph in 2a with two lines
   where each represents house_price_index
   and unemploy_perc over the years for each state. Once you have the
   chart, please comment on it as to whether it’s a good graph to
   present those two pieces of information.
```{r , echo=TRUE}
#facet_wrap
ggplot(data=house_reshaped, aes(x=date, y=value, color=measure), size=1) +
  geom_line() +
  geom_point() +
  facet_wrap(~state) +
  scale_y_continuous(
    name = "Value",
  ) +
  scale_x_date(
    name = "Year",
    breaks = ymd(c("1980-01-01", "2000-01-01", "2020-01-01")),
    labels = c("'80", "'00", "'20"),
    expand = c(.1, 0)
  ) +
  coord_cartesian(clip = "on") 

#facet_geo
ggplot(data=house_reshaped, aes(x=date, y=value, color=measure), size=1) +
  geom_line() +
  geom_point() +
  facet_geo(~state, grid = "us_state_grid1") +
  scale_y_continuous(
    name = "Value",
  ) +
  scale_x_date(
    name = "Year",
    breaks = ymd(c("1980-01-01", "2000-01-01", "2020-01-01")),
    labels = c("'80", "'00", "'20"),
    expand = c(.1, 0)
  ) +
  coord_cartesian(clip = "on") 
```
#(d) When you achieve the goals above, please create a R markdown file
#   and create an HTML page which has your codes and charts including
#   your comments.


